Notebook with AMP-AD RNA-seq network analysis results

### 2020-01-12 manuscript.Rmd
some figure updates

```{r}
synapser::synLogin()
AMPAD::pairwiseMatrixOfEnrichments('syn11932957')
```

@@

Plot from Figure 1c
```{r}
synapser::synLogin()
modMeta <- AMPAD::getModuleMetainfo('syn11932957')
dummyDf <- targetedEnrichment$cell
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf$category <- gsub('Zhang\\.','',dummyDf$category)
dummyDf$category <- factor(dummyDf$category,levels = rev(c('Astrocyte',
                                                       'Endothelial',
                                                       'Microglia',
                                                       'Neuron',
                                                       'MyelinOligos',
                                                       'NewOligos',
                                                       'OPC')))
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Cell Type Signature')
g
```

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Lake et al. Cell Type Signature')
g
```

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='CommonMind Differentially Expressed Module')
g
```

@@

```{r}
dummyDf <- targetedEnrichment$mssm2
dummyDf <- dplyr::filter(dummyDf,category == 'Yellow' | category == 'Pink' | category == 'Gray.1' | category == 'Seashell' | category == 'Red.3' | category == 'Green.yellow' | category == 'Red' | category == 'Gold.2' | category == 'Tan' | category == 'Gold.3' | category == 'Light.yellow' | category == 'Brown.2' | category == 'Dark.cyan' | category == 'Khaki' | category == 'Grey.60' | category == 'Purple' | category == 'Green.4' | category == 'Honey.dew' | category == 'Red.2' | category == 'Beige')
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Zhang et al. Module')
g
```

@@

```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
dummyDf$category <- factor(dummyDf$category,
                           levels = rev(c('genecards',
                                       'pantherPresenilin',
                                       'dbgap',
                                       'igap',
                                       'jensenDisease',
                                       'omimExpanded',
                                       'biocarta',
                                       'wikipathwaysMouse',
                                       'wikipathwaysHuman',
                                       'pantherAmyloid',
                                       'kegg',                                       
                                       'omim',
                                       'Nominated_targets',
                                       'MSSM',
                                       'Mayo_simple',
                                       'Mayo_comprehensive',
                                       'Emory',
                                       'Columbia_Broad_Rush_m109')))
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='AD Signature')
g

@@

>>>>

```{r}
synapser::synLogin()
AMPAD::pairwiseMatrixOfEnrichments('syn11932957')
AMPAD::pairwiseMatrixOfEnrichments('syn11932957',
                                   outputFile = T,
                                   fileName1 = '~/Desktop/updatedFiguresJan72020/figure1b.tiff')
```

@@

Plot from Figure 1c
```{r}
synapser::synLogin()
modMeta <- AMPAD::getModuleMetainfo('syn11932957')
dummyDf <- targetedEnrichment$cell
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf$category <- gsub('Zhang\\.','',dummyDf$category)
dummyDf$category <- factor(dummyDf$category,levels = rev(c('Astrocyte',
                                                       'Endothelial',
                                                       'Microglia',
                                                       'Neuron',
                                                       'MyelinOligos',
                                                       'NewOligos',
                                                       'OPC')))
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Cell Type Signature')
g
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Cell Type Signature',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresJan72020/figure1c.tiff')
```

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Lake et al. Cell Type Signature')
g
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Lake et al. Cell Type Signature',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresJan72020/figureS2b.tiff')
```

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='CommonMind Differentially Expressed Module')
g
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='CommonMind Differentially Expressed Module',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresJan72020/figures6b.tiff')

@@

```{r}
dummyDf <- targetedEnrichment$mssm2
dummyDf <- dplyr::filter(dummyDf,category == 'Yellow' | category == 'Pink' | category == 'Gray.1' | category == 'Seashell' | category == 'Red.3' | category == 'Green.yellow' | category == 'Red' | category == 'Gold.2' | category == 'Tan' | category == 'Gold.3' | category == 'Light.yellow' | category == 'Brown.2' | category == 'Dark.cyan' | category == 'Khaki' | category == 'Grey.60' | category == 'Purple' | category == 'Green.4' | category == 'Honey.dew' | category == 'Red.2' | category == 'Beige')
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Zhang et al. Module')
g

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='Zhang et al. Module',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresJan72020/figures6c.tiff')
```

@@

```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
dummyDf <- dplyr::filter(dummyDf,category!='Nominated_targets' & category!='Mayo_simple' & category != 'omim')

dummyDf$category <- gsub('Mayo_comprehensive',
                         'Mayo_RNAseq',
                         dummyDf$category)
# dummyDf$category <- factor(dummyDf$category,
#                            levels = rev(c('genecards',
#                                        'pantherPresenilin',
#                                        'dbgap',
#                                        'igap',
#                                        'jensenDisease',
#                                        'omimExpanded',
#                                        'biocarta',
#                                        'wikipathwaysMouse',
#                                        'wikipathwaysHuman',
#                                        'pantherAmyloid',
#                                        'kegg',                                       
#                                        'omim',
#                                        'Nominated_targets',
#                                        'MSSM',
#                                        'Mayo_simple',
#                                        'Mayo_comprehensive',
#                                        'Emory',
#                                        'Columbia_Broad_Rush_m109')))

dummyDf$category <- factor(dummyDf$category,
                           levels = rev(c('genecards',
                                       'pantherPresenilin',
                                       'dbgap',
                                       'igap',
                                       'jensenDisease',
                                       'omimExpanded',
                                       'biocarta',
                                       'wikipathwaysMouse',
                                       'wikipathwaysHuman',
                                       'pantherAmyloid',
                                       'kegg',                                       
                                       'MSSM',
                                       'Mayo_RNAseq',
                                       'Emory',
                                       'Columbia_Broad_Rush_m109')))

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='AD Signature')
g

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='AD Signature',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresJan72020/figure1d.tiff',
                 scaleValue = 2)
```

@@

g<-AMPAD::make_dot_plot(dummyDf,
                 xlab='AD Coexpression Module',
                 ylab='DEG Sex Specific Meta Analysis',
                 outputFile = TRUE,
                 fileName = '~/Desktop/updatedFiguresJan72020/figure4d.tiff')
```
